---
title: "Raw data, tidy data, and Codebook"
description: |
  Overview the collected data across languages and laboratory settings.
#theme: theme.css
#date: "`r Sys.Date()`"
#output: distill::distill_article
---

```{r setup, include=FALSE, code = readLines("init.R"), cache=TRUE, cache.path="./catch/"}
knitr::opts_chunk$set(echo = FALSE)
```

### Raw data files

The all raw data were uploaded to the[project OSF](https://osf.io/2zxrw/). We will make the raw data public once we submit the final report to PB&R.

<!---
accessible links...
--->

### Tidy data files

The example analysis in this website were from the tidy data files. Researchers would access the data files by the subtitles.

#### [Sentence-Picture verification](includes/files/SP_V_tidy.csv)

```{r SP_V_code, echo=FALSE}
codebook::compact_codebook(read_csv("./includes/files/SP_V_tidy.csv"))
```



#### [Picture-Picture verification](includes/files/PP_tidy.csv)


```{r PP_code, echo=FALSE}
codebook::compact_codebook(read_csv("./includes/files/PP_tidy.csv"))
```
